---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Lindsay Stall"
date: "3/28/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

```{r}
m_bty <- lm(score ~ bty_avg, data=evals)
summary(m_bty)
```
y = 0.6664x + 3.88

R-squared:  0.03502
Adjusted R-squared:  0.03293

### Exercise 2
```{r}
m_bty_gen <- lm(score ~ bty_avg + gender, data=evals)
```

```{r}
summary(m_bty_gen)
```
y = 0.07416x + 0.17239z + 3.75

R-squared: 0.05912
Adjusted R-squared: 0.05503

### Exercise 3

Intercept = 3.7434, that would be the score if the beauty was 0 and the gender was female
.07416 is how much the score would go up for every 1 increase of beauty
.17239 is the amount that male professors score higher than females on average

### Exercise 4

The variability is 5.5503%


### Exercise 5

y= .07416x + (.17239 + 3.74734)


### Exercise 6

Males

### Exercise 7

Males will generally have higher scores


### Exercise 8

The adjusted r-squared for the equation with gender explains more variance than without. In particular, adding it increases the variance explained % by 22%.

### Exercise 9

Yeah, it raised by about .01

### Exercise 10



### Exercise 11




### Exercise 12




### Exercise 13



### Exercise 14



### Exercise 15



### Exercise 16



### Exercise 17




### Exercise 18





